Index measures for oak decline severity using phenotypic descriptors

### 2019-12-14 manuscript/manuscript.Rmd
removed crown surface area and crown production efficiency

```{r loadData, include = FALSE}
loadd(site_rf_margin,
      site_rf_post_correction_margin,
      PDI_status_ttest,
      DAI_groups_ttest,
      PDI_rf_tune_params,
      DAI_rf_tune_params,
      site_corrected_analysis_suitable_data)
```

@@

Seven additional, composite descriptors were calculated to account for the three dimensional attributes of the tree and covariate nature of certain descriptors as suggested by @zarnoch2004.
This then gave a total of 38 raw and composite phenotypic descriptors.
The additional descriptors are defined as follows:

@@

**Composite crown surface area (m^2^)** - Estimated crown surface area proportional to crown condition. Adapted from @laroque1994.

$$S = \frac{4\pi(h-l)}{3r^2} \left[ \left( r^2 + \frac{r^4}{4(h-l)^2} \right) ^{1.5} - \left( \frac{r^4}{4(h-l)^2} \right) ^{1.5} \right] \times c $$

**Crown production efficiency** - Estimate of crown production efficiency as a ratio between the composite crown surface area and the composite crown volume [@zarnoch2004].

$$e = \frac{S}{v}$$

>>>>

```{r loadData, include = FALSE}
loadd(site_rf_margin,
      site_rf_post_correction_margin,
      PDI_status_ttest,
      DAI_groups_ttest,
      PDI_rf_tune_params,
      DAI_rf_tune_params,
      analysis_suitable_data,
      site_corrected_analysis_suitable_data)
```

@@

Five additional, composite descriptors were calculated to account for the three dimensional attributes of the tree and covariate nature of certain descriptors as suggested by @zarnoch2004.
This then gave a total of `r ncol(analysis_suitable_data)` raw and composite phenotypic descriptors.
The additional descriptors are defined as follows:

@@
